# Main findings {#section5}

As mentioned above, this Preparedness Diagnostic uses four dimensions analysis as a reference. Each dimension contains elements considered relevant to have an "Ideal RBM System". This Ideal RBM System will allow us to compare the current situation in Dominica in relation to the best possible scenario regarding RBM, its practices, uses and results. Figure 5 shows the progress rate of  each of the dimensions analysed, with respect to the ideal scenario.

The elements and sub-elements of the reference Ideal RBM System are not a “natural” condition. This means that each one must be designed and developed; following this, a country that has not considered adopting RBM practices would probably not comply or show advances in any of the analysed elements. In this sense, all the advances identified in this diagnosis represent valuable progress.

It is important to mention that, although there is a numerical value for each dimension, behind the numbers there was a qualitative analysis that determined the current situation of Dominica regarding RBM. Furthermore, these "ratings" are in terms of the ideal scenario, so in no way does it represent an outright success or failure, but rather a proxy to the best possible situation of the RBM.

```{r, include=FALSE}
source("radar.R", local = knitr::knit_global())

data <- filter(radar, order == 3)

# To use the fmsb package, I have to add 2 lines to the dataframe: the max and min of each topic to show on the plot
  
data <- rbind(rep(100,4) , rep(0,4) , select(data, -country, -order))

```

<center>
+---------------------------+------------------------+
| DIMENSION                 | LEVEL OF PROGRESS      | 
+===========================+========================+
| INSTITUTIONALISATION      |    22%      | 
+---------------------------+-------------+
| EXECUTION FRAMEWORK       |    9%      | 
+---------------------------+-------------+
| TECHNICAL CAPABILITIES    |    28%      | 
+---------------------------+-------------+
| USE OF EVIDENCE           |    14%     | 
+---------------------------+-------------+

Table: (\#tab:table) Developed by the CLEAR LAC technical team in charge of the collaboration
</center>

```{r figure5, echo = FALSE, fig.cap = "Level of progress of the Ideal RBM System", out.width = '70%',fig.align = 'center'}
radar_rbm( data[1:3,], colors_border[3,], colors_in[3,], whole = TRUE )
```

Considering this level of progress, a metric was built to progressively identify five levels of maturity of RBM systems. In this way, the progress levels presented above are averaged to characterise the Member State’s level . The 5 levels are:

  1.	Early initiatives
  2.	Committed development
  3.	Growing RBM System
  4.	Consolidated practices
  5.	Mature State

Based on the results from the Preparedness Diagnostic analysis, Dominica is currently in the Early initiatives level. Significant efforts have been made in developing and implementing a results-oriented national planning with clear strategies that contribute to the achievement of Dominica’s higher goal of climate resiliency. There are also initial efforts in monitoring activities; however, they are not articulated and there are no clear responsible stakeholders in the monitoring process. It is pending for Dominica to start the drafting of an RBM Policy and the building of a whole-of-government, to develop evaluation activities, to define an incentives structure to build an enabling environment that ensures the sustainability of an RBM System.


##	Results by dimension 

The results of this diagnosis for each of the dimensions analysed (and their ideal elements) are presented below in a synthetic manner. For more detailed information on each dimension, elements, and sub-elements, please see [appendix C](#appendixC) and visit the interactive platform with all the disaggregated findings of this PD.


```{r , include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

### Institutionalisation 

:::dim1
**Key Message:**
Dominica has broad normative frameworks in planning, significant advances in budgeting, and slight advances in monitoring.The Climate Resilience Executive Agency for Dominica (CREAD), a cross-cutting and temporary institution created to achieve Dominica's long-term goal (become the first climate resilient nation), plays a relevant role in supporting MDAs in the monitoring and implementation of programmes. However, there are not enough norms and clear responsibilities to foster the continuous improvement in planning, budgeting, and implementation based on the use of M&E results, and to articulate a whole of government RBM system.
:::

```{r , echo=FALSE, results="asis"}
library(readxl)
library(kableExtra)
library(dplyr)


results <- read_excel("./Data/results.xlsx")

dim_1 <-  results %>% 
          filter( dimension_id == 1) %>% 
          select( -dimension, -dimension_id, -element_id ) 

kable(dim_1) %>%
          kable_paper("striped", full_width = T, font_size = 14) %>%
          column_spec(1, bold = T, border_right = T) %>%
          column_spec(2, width = "33em")
          

```


### Execution Framework 

:::dim2
**Key Message:**
The Ministry of Planning gathers monthly reports from all the MDAs regarding their performance. Also, both national planning documents (NRDS and CRRP) have monitoring frameworks. However, these monitoring exercises are not structured in a clear process and are not articulated. There is no common language among MDAs around M&E as well as no M&E network to perform M&E activities.  Also, there is no transparency regarding the monitoring activities and the results.
:::




```{r , echo=FALSE, results="asis"}
dim_1 <-  results %>% 
          filter( dimension_id == 2) %>% 
          select( -dimension, -dimension_id, -element_id ) 

kable(dim_1) %>%
          kable_paper("striped", full_width = T, font_size = 14) %>%
          column_spec(1, bold = T, border_right = T) %>%
          column_spec(2, width = "33em")
          

```


### Technical capabilities


:::dim3
**Key Message:**
There are skills to conduct planning, budgeting, and monitoring for results. The creation of CREAD and the development of the CRRP has translated the national's planning into action with clear priorities and targets to be achieved. The national budgeting function is fulfilled based on the collaboration between planning and finance. Also, ministries such as planning conduct regular monitoring, coordinating with the other MDAs. However, these skills are not homogeneous among MDAs.
:::


```{r , echo=FALSE, results="asis"}

dim_1 <-  results %>% 
          filter( dimension_id == 3) %>% 
          select( -dimension, -dimension_id, -element_id ) 

kable(dim_1) %>%
          kable_paper("striped", full_width = T, font_size = 14) %>%
          column_spec(1, bold = T, border_right = T) %>%
          column_spec(2, width = "33em")
          

```


### Use of evidence


:::dim4
**Key Message:**
There are skills to conduct planning, budgeting, and monitoring for results. The creation of CREAD and the development of the CRRP has translated the national's planning into action with clear priorities and targets to be achieved. The national budgeting function is fulfilled based on the collaboration between planning and finance. Also, ministries such as planning conduct regular monitoring, coordinating with the other MDAs. However, these skills are not homogeneous among MDAs.
:::


```{r , echo=FALSE, results="asis"}

dim_1 <-  results %>% 
          filter( dimension_id == 4) %>% 
          select( -dimension, -dimension_id, -element_id ) 

kable(dim_1) %>%
          kable_paper(c("hover"), full_width = T, font_size = 14) %>%
          column_spec(1, bold = T, border_right = T) %>%
          column_spec(2, width = "33em")
          

```

##	Main challenges to strengthen the RBM system

As mentioned in section 2.2, the development of an RBM System is a complex, nonlinear, and continuous process that must be contextualized in each country. In doing so, it is important to consider the main challenges that Dominica faces when it comes to strengthening its RBM system. This diagnosis identifies three major challenges:

1.	Changing the culture and fostering the enabling environment to have an RBM system in place implies a change of mindset of public servants at all levels. It should be considered that throughout the process there must be a constant awareness/sensitization strategy, both in the short and medium term, that allows public servants to identify the importance to have this mindset change in pursuit of RBM. In other words, on a regular basis,  there needs to be reminders on the importance of RBM and its impact on improving performance and lives of all citizens

2.	Since this collaboration constitutes a whole-of-government approach, it is necessary to have a top-bottom commitment in which leaders and decision-makers demonstrate the benefits of the RBM system through evidence informed actions that are generated by the RBM system. This means that we need a top-bottom approach to use, and thereby demonstrate its usefulness, the information and evidence derived from the RBM system to improve planning and budgeting decisions.

3.	For the RBM system to be sustainable, it is critical to generate a system of incentives and ensure that there is a balance between positive and negative incentives (such as potential penalties for non-compliance), to advance and sustain the system. The positive incentives can take different forms, from monetary to symbolic, such as the presentation of awards to staff and units and recognition for good performance in public service.





